The Driving Forces of API Evolution

### 2015-05-25 thesis/paper.tex
Table of meth

@@

%How the initial inspection was performed
The API code was inspected sequentially, starting with v1.4. Both versions of the API underwent the same inspection. This involved extracting method signatures, enums, structs, typedefs and macros, which were subsequently stored in spreadsheets. The extraction involved a lot of manual work, but Git's \cite{git} diff command was used to identify changes in files which exist in both versions. After a change was identified in the code, a description of the corresponding change in the documentation was added to the spreadsheet. The module and file in which the change was identified was then logged together with an ID and a description of the change. The data collection from code and documentation was performed independently by both John Burchell and William Granli, to reduce the risk of human errors affecting the results. If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.

>>>>

\begin{table}
       \centering
       \begin{tabular}[ht]{p{3in}}
              \toprule

              \begin{enumerate}
              \item Inspect source code  
              \item Inspect accompanying documentation 
              \item Generate Hypotheses 
              \item Conduct Interview 
              \item Analyse source code 
              \item Analyse interviews 
              \item Classify trends according to types 
              \item Compare classifications against interview responses 
              \item Analyse from software evolution theory point of view 
              \item Validate Hypotheses 
              \end{enumerate} \\
              \bottomrule
       \end{tabular}
       \caption{Methodology Steps}
       \label{table:meth_steps}
\end{table}

@@

%How the initial inspection was performed
The API code was inspected sequentially, starting with v1.4. Both versions of the API underwent the same inspection. This involved extracting method signatures, enums, structs, typedefs and macros, which were subsequently stored in spreadsheets. The extraction involved a lot of manual work, but Git's \cite{git} diff command was used to identify changes in files which exist in both versions. After a change was identified in the code, a description of the corresponding change in the documentation was added to the spreadsheet. The module and file in which the change was identified was then logged together with an ID and a description of the change. The data collection from code and documentation was performed independently by both researchers to reduce the risk of human errors affecting the results. If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.
